##  DATA CLARIFICATION
##
##  Input: cpu-clean.csv
##  Output: None
##
##
##  Description:
##
##  Caveats:
##
##  NK
##  ---

PART 1. Attributes' distribution.


```{r}
pacman::p_load(
  rio,     # for imports & exports
  ggplot2, # for plots
  zoo      # for year-quarter formats
)
##  IMPORT THE DATA
setwd("/Users/admin/Desktop/_probability_PROJECT/btlprob/rcode")   # set working directory
data <- import("cpu-clean.csv")        # rio::import
```

# draw piechart for markettable
# should write some percentages too
# we can see what constitue the most marketshare
# Mobile & Desktop & Server were targetted market of Intel.
```{r}
pie(as.vector(table(data$market)), levels(factor(data$market)))
```

# Draw stacked column histogram for status ~ ldate (STUCK)
# how many chips shutdown, supported, launched in each quarter?
# TO-DO: There are so many EOL products in 2012-2013, why?
# TO-DO: Try plotting EOL distribution -> and see
```{r}
ggplot(data = data, aes(x = data$ldate)) +
  geom_histogram(aes(fill = data$status))
```

# Draw histogram for litho
# there are some cpus having very high lithography, which come from older era, 
# they can be considered as outliners.
# Let's see what is the common range of lithography
```{r}
boxplot(data$litho)
hist(data$litho)
summary(data$litho)
```

# rprice for each market
# many outliners can be seen for each kind of market
# when analyzing them, we will perform further cleaning methods
```{r}
hist(data$rprice[data$market == "Mobile"])
hist(data$rprice[data$market == "Desktop"])
hist(data$rprice[data$market == "Embedded"])
hist(data$rprice[data$market == "Server"])
```

# ncore for each market
```{r}
hist(data$ncore[data$market == "Mobile"])
hist(data$ncore[data$market == "Desktop"])
hist(data$ncore[data$market == "Embedded"])
hist(data$ncore[data$market == "Server"])
```
# !!! POTENTIAL HYPOTHESIS TESTING BETWEEN nCore and rPrice : are they the same?



# nthread ~ ncore ??
# !!! POTENTIAL HYPOTHESIS TESTING BETWEEN : is the nthread = 2*ncore ???? is it dominant ???

# bfreq
# Does it follow the Normal distribution?
```{r}
hist(data$bfreq)
```

# tdp
# most cpu on the market has tdp value in the following range, a few exceptions can be seen.
```{r}
hist(data$tdp)
boxplot(data$tdp)
summary(data$tdp)
```





# memband
# the memband's variance is very low
```{r}
boxplot(data$memband)
```


# temp
```{r}
hist(data$temp)
```










PART 2. Relationship between features.






# ncore ~ ldate
# Increasing?
```{r}
plot(ncore ~ ldate, data=data)
```

# litho ~ ldate
# Decreasing, getting better?
```{r}
plot(litho ~ ldate, data=data)
```



# rprice ~ ldate (DEPRECATED - No clear trend)
```{r}
plot(rprice ~ ldate, data=data)
```


```{r}
table(factor(data$market))
```


