##  DATA CLARIFICATION
##
##  Input: cpu-clean.csv
##  Output: None
##
##
##  Description: 
##
##  Caveats: DO NOT CHANGE THE NUMBER OF LINES IN THIS FILE
##
##  NK
##  ---

PART I. OVERVIEW OF THE attributeS

LOADING PACKAGES & IMPORTING DATA
```{r}
pacman::p_load(
  rio,     # for imports & exports
  ggplot2, # for plots
  zoo      # for year-quarter formats
)
##  IMPORT THE DATA
setwd("/Users/admin/Desktop/_probability_PROJECT/btlprob/rcode")   # set working directory
data <- import("cpu-clean.csv")        # rio::import
```

CATEGORIAL PIES
```{r}
# Config market pie
freq = as.vector(table(data$market))
levels = levels(factor(data$market))
title = "market"
```

```{r}
# Config status pie
freq = as.vector(table(data$status))
levels = levels(factor(data$status))
title = "status"
```

```{r}
# Drawing the pie
# Calculate the vector of percentages
percentages <- round(
  100 * freq / sum(freq), 
  1
  )

# Create the data frame of levels, frequency of values, and percentages
data_percentages <- data.frame(
  market = levels, 
  value = freq, 
  percent = percentages
  )

# Create a pie chart with percentages
ggplot(
  data_percentages, 
  aes(x="", y=value, fill=market)) +
  geom_bar(stat="identity", width=1, color="white") + # Draw the bar
  coord_polar(theta = "y") +               # Representing the values in polar
                                           # coordinate. Instead of stacked bars
  # Add labels (percentage numbers)
  geom_text(
    aes(label = paste0(percent, "%")),     # Concat 'percent' + '%'
    position = position_stack(vjust = 0.5) # Each slide is a stack bar
                                           # Use position_stack to stack the labels
                                           # on each slide.
    ) +
  labs(fill = title) +
  theme_void()
```

Histogram of launch date
```{r}
ggplot(data, aes(x = ldate)) +
  geom_histogram(binwidth = 1, fill="deepskyblue") +
  labs(x = "Date", y = "Count")                      # Label of axes
```

Boxplot of Lithography
```{r}
ggplot(data, aes(x = market, y = litho)) +
  geom_boxplot(fill="deepskyblue") +
  labs(x = "Market", y = "Lithography (nm)")

summary(data$litho)
```

Scatter plot of Lithography
```{r}
ggplot(data, aes(x = ldate, y = litho)) +
  geom_point(color="deepskyblue") +
  labs(x = "Launch Date", y = "Lithography (nm)")
```

Boxplot of Recommended Price
```{r}
ggplot(data, aes(x = market, y = rprice)) +
  geom_boxplot(fill="deepskyblue") +
  labs(x = "Market", y = "Recommended Price ($)")
```

Histogram of Base frequency
```{r}
ggplot(data, aes(x = bfreq)) +
  geom_histogram(binwidth = 0.1, fill="deepskyblue") +
  labs(x = "Base frequency (GHz)", y = "Count")
```

Histogram of Thermal Design Power
```{r}
ggplot(data, aes(x = market,y = tdp)) +
  geom_boxplot(fill="deepskyblue") +
  labs(x = "Market", y = "Thermal deisgn power (W)")

summary(data$tdp)
```

Histogram of Memmory Bandwith (HIDDEN IN OUR REPORT)
```{r}
ggplot(data, aes(y = memband)) +
  geom_boxplot(fill="deepskyblue") +
  labs(x = "Max Memory Bandwidth (GB/s)", y = "Count")

summary(data$memband)
```

Histogram of Temperature (HIDDEN IN OUR REPORT)
```{r}
ggplot(data, aes(x = temp)) +
  geom_histogram(binwidth = 1, fill="deepskyblue") +
  labs(x = "Temperature (°C)", y = "Count")
```

# NOTE, PLEASE DO NOT CHANGE ANYTHING ABOVE THIS LINE
# ---------------------------------------------------









PART 2. ANALYSIS OF attributes

[bfreq & ncore ~ tdp]

We plot the distribution of Thermal Design Power as histogram.
And cut the outliners
```{r}
ggplot(data, aes(x = tdp)) +
  geom_histogram(binwidth = 5, fill="deepskyblue")

# Data after cut the outliners of TDP
data2 <- data[data$tdp < 150, ]

# 
```

Now we will find out, on what attribute that TDP actually depends on.

Test for market ~ tdp
```{r}
ggplot(data, aes(x = market,y = tdp))+
  geom_boxplot(fill="deepskyblue")

# We see that the distribution of Desktop and Server is approximately the same.
# We will cut the data, containing only Desktop and Server, to perform ANOVA test on it.
data2 <- subset(data2, data2$market %in% c("Desktop","Server"))

ggplot(data2, aes(x = market,y = tdp))+
  geom_boxplot(fill="deepskyblue")

ggplot(data2, aes(x = tdp)) +
  geom_histogram(binwidth = 10, fill="deepskyblue") + 
  facet_wrap(~data2$market)
```





















```{r}
# We plot the histogram of litho ~ bfreq
ggplot(data, aes(x = tdp)) +
  geom_histogram(binwidth = 0.1, fill="deepskyblue") + 
  facet_wrap(~data$litho)

# We see that some categories of lithography are not significant in terms of
# quantity, and do not follow any clear distribution. We will treat them as
# outliners.

# We choose to keep the following category:
# 14, 22, 32, 45:
data <- subset(data, data$litho %in% c(14,22,32,45))

# We plot the histogram of ncore ~ bfreq
ggplot(data, aes(x = bfreq)) +
  geom_histogram(binwidth = 2, fill="deepskyblue") + 
  facet_wrap(~data$ncore)

# We see that some categories of ncore are not significant in terms of quantity
# -> remove it too

# We choose to keep the following category:
# 2, 4
data <- subset(data, data$ncore %in% c(2,4))

# Group them as factors
data$ncore <- as.factor(data$ncore)
data$litho <- as.factor(data$litho)

# Now, we visualize all of this up, to see what did we get so far:
ggplot(data, aes(x = ncore,y = bfreq,color = litho))+
  geom_boxplot()
```




ANOVA - one way [litho ~ bfreq when ncore = 4]

Since the variance and normality is not perfect, we better do a non-parametric test,
such as Kruskal–Wallis one-way analysis of variance.

We can see that the values of the test is small (< 0.05), we can say that there are significant differences between the
"ranks" (<- explain this further)
```{r}
ggplot(data, aes(x = litho,y = bfreq))+
  geom_boxplot(fill = "deepskyblue")
kruskal.test(bfreq ~ litho, data = data)
```

To see which group is significantly different from others, we must perform a
post-hoc comparison, in this case, we use Wilcoxon test
[https://en.wikipedia.org/wiki/Kruskal%E2%80%93Wallis_one-way_analysis_of_variance]
```{r}
pairwise.wilcox.test(data$bfreq, data$litho, p.adjust.method = "bonferroni")
```



ANOVA - one way (ncore ~ bfreq)

```{r}
# OK YOU GET THE IDEA, PLEASE DO THAT FOR ME VIETTUNG
```




ANOVA - two way [litho & ncore ~ bfreq]

Now we construct Two-way ANOVA model
```{r}
model<- aov(bfreq ~ litho * ncore ,data = data)
qqPlot(residuals(model))
shapiro.test(residuals(model))
leveneTest(bfreq ~ litho *  ncore ,data = data)
Anova(model, type='III')
```


Transform the data to rank-based. Nonparametric Two-way ANOVA
"Finaly, let’s perform two-way ANOVA on the rank-transformed data. Ranking is one of many procedures used to transform data that do not meet the assumptions of normality. Conover and Iman (1981) provided a review of the four main types of rank transformations. One method replaces each original data value by its rank (from 1 for the smallest to N for the largest, where N is the combined data sample size)"
[https://www.cfholbert.com/blog/nonparametric_two_way_anova/]

As we can see, it looks worse.
```{r}
model<- aov(rank(bfreq) ~ litho * ncore ,data = data)
qqPlot(residuals(model))
shapiro.test(residuals(model))
leveneTest(rank(bfreq) ~ litho *  ncore ,data = data)
Anova(model, type='III')
```

One frustrating thing about tests is that they are very sensitive to large data.
So do not trust in tests, but the intuition.















































